Epilepsy GLMM example

### 2023-02-14 src/epil/epil.Rmd
Fix missing + sign

plot_pdf_stan_aghq <- plot_pdf_stan_aghq +
    geom_line(data = laplace_x[[1]]$pdf_and_cdf, aes(x = theta, y = pdf), col = cbpalette[2]) +
    lims(x = c(1.2, 2)) +
    labs(title = "Inference from aghq and custom Laplace method")
    theme_minimal()

(plot_intercept_comparison <- plot_pdf_stan_inla/ plot_pdf_stan_aghq)

>>>>

plot_pdf_stan_aghq <- plot_pdf_stan_aghq +
    geom_line(data = laplace_x[[1]]$pdf_and_cdf, aes(x = theta, y = pdf), col = cbpalette[2]) +
    lims(x = c(1.2, 2)) +
    labs(title = "Inference from aghq and custom Laplace method") +
    theme_minimal()

plot_intercept_comparison <- plot_pdf_stan_inla / plot_pdf_stan_aghq

plot_intercept_comparison
